---
title: "prepare EGFP seurat obj"
author: "Yifang Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    code_folding: hide
    fig_width: 10
    fig_height: 10
    highlight: kate
    thumbnails: false
    lightbox: true
    gallery: true
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

options(max.print = 200)
opts_chunk$set(echo = TRUE,
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               dev = c('png', 'pdf'),
               fig.width = 10,
               fig.height = 10,
               fig.align = "center",
               fig.path = 'PDF_2020-02-05_prepare_EGFP_seurat_obj/',
               dpi = 72)
opts_knit$set(width = 75)
```

```{r setup}
set.seed(123)

npc <- 20
# theta1 <- 2
# theta2 <- 5
# theta <- c(theta1, theta2)
resolution <- 0.1
pt_size <- 1

# Suppress loading messages
suppressPackageStartupMessages({
  library(Matrix)
  library(dplyr)
  library(tidyverse)
  library(Seurat)
  library(cowplot)
  library(Rcpp)
  library(harmony)
  library(SoupX)
})
```

# Harmony

```{r}
# initialize
EGFP <- readRDS("Data/2020-02-05_EGFP_matrix.Rds")
EGFP <- CreateSeuratObject(counts = EGFP, project = "EGFP")
EGFP <- NormalizeData(EGFP, verbose = FALSE)
EGFP <- FindVariableFeatures(EGFP, selection.method = "vst", nfeatures = 2000)
all_genes <- rownames(EGFP)
EGFP <- ScaleData(EGFP, features = all_genes, verbose = FALSE)
EGFP <- RunPCA(EGFP, features = VariableFeatures(object = EGFP), npcs = npc, verbose = FALSE)

# metadata
EGFP$percent_mito <- PercentageFeatureSet(EGFP, pattern = "^mt:")
EGFP$log2nGene <- log2(EGFP$nFeature_RNA)
EGFP$log2nUMI <- log2(EGFP$nCount_RNA)

# EGFP$Condition <- c(
#   rep("EGFP", sum(
#     sum(grepl("G0", colnames(EGFP))),
#     sum(grepl("G1", colnames(EGFP)))
#   )),
#   rep("TSC1", sum(
#     sum(grepl("T0", colnames(EGFP))),
#     sum(grepl("T1", colnames(EGFP)))
#   ))
# )

# my_levels <- c("EGFP", "TSC1")

# EGFP$Condition <- factor(x = EGFP$Condition, levels = my_levels)

# EGFP$LibraryID <- c(
#   rep("G0", sum(grepl("G0", colnames(EGFP)))),
#   rep("G1", sum(grepl("G1", colnames(EGFP)))),
#   rep("T0", sum(grepl("T0", colnames(EGFP)))),
#   rep("T1", sum(grepl("T1", colnames(EGFP))))
# )
# 
# my_levels <- c("G0", "G1", "T0", "T1")
# 
# EGFP$LibraryID <- factor(x = EGFP$LibraryID, levels = my_levels)

EGFP$LibraryID <- c(
  rep("G0", sum(grepl("G0", colnames(EGFP)))),
  rep("G1", sum(grepl("G1", colnames(EGFP))))
)

my_levels <- c("G0", "G1")

EGFP$LibraryID <- factor(x = EGFP$LibraryID, levels = my_levels)

# EGFP$Batch <- c(
#   rep("Batch0812", sum(grepl("G0", colnames(EGFP)))),
#   rep("Batch0819", sum(grepl("G1", colnames(EGFP)))),
#   rep("Batch0812", sum(grepl("T0", colnames(EGFP)))),
#   rep("Batch0819", sum(grepl("T1", colnames(EGFP))))
# )
# 
# my_levels <- c("Batch0812", "Batch0819")
# 
# EGFP$Batch <- factor(x = EGFP$Batch, levels = my_levels)

write.csv(EGFP@meta.data, file = "Data/2020-02-05_EGFP_metadata.csv")

# RunHarmony

# EGFP <- EGFP %>%
#   RunHarmony(c("Condition", "Batch"), theta = theta, plot_convergence = FALSE, max.iter.harmony = 20)

EGFP <- EGFP %>%
  RunHarmony("LibraryID", plot_convergence = FALSE, max.iter.harmony = 20)

EGFP <- EGFP %>%
  RunUMAP(reduction = "harmony", dims = 1:npc) %>%
  RunTSNE(reduction = "harmony", dims = 1:npc) %>%
  FindNeighbors(reduction = "harmony", dims = 1:npc, verbose = FALSE, force.recalc = TRUE) %>%
  FindClusters(resolution = seq(0.1, 1, 1), verbose = FALSE) %>%
  identity()

saveRDS(EGFP, file = "Data/2020-02-05_EGFP_seurat_obj.Rds")
```

# Condition / Batch / LibraryID / log2nGene / log2nUMI / Percent mito - UMAP {.tabset}

<!-- ## Condition -->

<!-- ```{r Condition_umap} -->
<!-- DimPlot(EGFP, reduction = "umap", group.by = "Condition", pt.size = pt_size) -->
<!-- ``` -->

<!-- ## Batch -->

<!-- ```{r Batch_umap} -->
<!-- DimPlot(EGFP, reduction = "umap", group.by = "Batch", pt.size = pt_size) -->
<!-- ``` -->

## LibraryID

```{r libraryid_umap}
DimPlot(EGFP, reduction = "umap", group.by = "LibraryID", pt.size = pt_size)
```

## log2nGene

```{r log2nGene_umap}
FeaturePlot(EGFP, reduction = "umap", features = c("log2nGene"), pt.size = pt_size)
```

## log2nUMI

```{r log2nUMI_umap}
FeaturePlot(EGFP, reduction = "umap", features = c("log2nUMI"), pt.size = pt_size)
```

## Percent mito

```{r percent_mito_umap}
FeaturePlot(EGFP, reduction = "umap", features = c("percent_mito"), pt.size = pt_size)
```

# UMAP - resolutions {.tabset}

In the UMAP embedding, we can see more intricate structure. Since we used harmony embeddings, the UMAP embeddings are well mixed.

```{r UMAP_resolutions, results = 'asis'}
for(res in seq(0.1, 1, 1)){
  cat("\n")
  cat("\n## ", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(EGFP) <- selected_res
  p <- DimPlot(EGFP, reduction = "umap", label = TRUE, pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# UMAP - Resolutions - Split {.tabset}

In the UMAP embedding, we can see more intricate structure. Since we used harmony embeddings, the UMAP embeddings are well mixed.

```{r umap_resolutions_split, results = 'asis'}
for(res in seq(0.1, 1, 1)){
  cat("\n")
  cat("\n## ", "Cluster resolution: ", res, "{.tabset}\n")
  selected_res <- paste0("RNA_snn_res.", res)
  Idents(EGFP) <- selected_res
  p <- DimPlot(EGFP, reduction = "umap", label = TRUE, split.by = "LibraryID", pt.size = pt_size)
  print(p)
  cat("\n")
}
```

# Notes

2020-02-05:

  * Only analysis EGFP.

Sat Nov 30, 2019:

  * prepare EGFP TSC1 seurat object.

Tue Oct 29, 2019:

  * use SoupX fixed 0.45 to remove ambient RNA.

Mon Oct 7, 2019:

  * Add more sequence depth.

Mon, Sep 30, 2019:

  * remove genes: EGFP, Tsc1, gig. Then perform integrate analysis of EGFP, TSC1.

Fri, Sep 20, 2019:

  * First version for integrate analysis of EGFP, TSC1.

# Session Info

```{r sessioninfo, message=TRUE}
sessionInfo()
```

