---
title: "6 miniViolin plots of known marker genes for all clusters"
author: "Yifang Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    code_folding: hide
    fig_width: 10
    fig_height: 10
    highlight: kate
    thumbnails: false
    lightbox: true
    gallery: true
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

options(max.print = 200)
opts_chunk$set(echo = TRUE,
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               dev = c("png", "pdf"),
               fig.width = 10,
               fig.height = 10,
               fig.align = "center",
               fig.path = "6_PDF_2020-02-05_miniViolin_plots_of_known_marker_genes_for_all_clusters/",
               dpi = 72)
opts_knit$set(width = 75)
```

```{r setup}
set.seed(123)

npc <- 20
# theta1 <- 2
# theta2 <- 5
# theta <- c(theta1, theta2)
resolution <- 0.1
selected_res <- paste0("RNA_snn_res.", resolution)
pt_size <- 1
# alpha <- 0.8

# Suppress loading messages
suppressPackageStartupMessages({
  library(Matrix)
  library(dplyr)
  library(tidyverse)
  library(Seurat)
  library(cowplot)
  library(Rcpp)
  library(harmony)
  library(SoupX)
})
```

```{r load_data}
EGFP <- readRDS("Data/2020-02-05_EGFP_seurat_obj.Rds")
Idents(EGFP) <- selected_res
```

# Markers Set1

```{r}
gene_list <- c(
  "LpR1",
  "FASN3",
  # "Ten-a",
  "salm",
  # "Lsd-2",
  "nmo",
  "AkhR",
  "daw",
  "mdy",
  "Pkn",
  "luna",
  "CG5151",
  "Mhc"
  # "MP2P"
)
```

# miniViolin

```{r miniViolin_set1}
for (gene in gene_list) {
  plot <- VlnPlot(EGFP, features = gene, pt.size = 0, combine = FALSE)
  p <- plot[[1]] +
    theme(legend.position = 'none') +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ylab(gene) +
    theme(plot.title = element_blank()) +
    theme(axis.text.y = element_text(size = 3)) +
    theme(text = element_text(size = 8))
  assign(gene, p)
}

plot <- VlnPlot(EGFP, features = "Ten-a", pt.size = 0, combine = FALSE)
Tena <- plot[[1]] +
    theme(legend.position = 'none') +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ylab("Ten-a") +
    theme(plot.title = element_blank()) +
    theme(axis.text.y = element_text(size = 3)) +
    theme(text = element_text(size = 8))

plot <- VlnPlot(EGFP, features = "Lsd-2", pt.size = 0, combine = FALSE)
Lsd2 <- plot[[1]] +
    theme(legend.position = 'none') +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ylab("Lsd-2") +
    theme(plot.title = element_blank()) +
    theme(axis.text.y = element_text(size = 3)) +
    theme(text = element_text(size = 8))
 
x_label <- plot[[1]] +
  theme(legend.position = 'none') +
  ylab("") +
  theme(plot.title = element_blank()) +
  theme(axis.text.y = element_text(size = 3)) +
  theme(text = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 20))

plot_grid(
LpR1,
FASN3,
Tena,
salm,
Lsd2,
nmo,
AkhR,
daw,
mdy,
Pkn,
luna,
CG5151,
Mhc,
# MP2P, 
x_label, ncol = 1)
```

# Markers Set2

```{r}
gene_list <- c(
"Mhc",
"Mp20",
"Act87E",
"Act57B",
"Mef2",
"Cyp4g1",
"Desat1",
"CG18609",
"CG17562",
"btl",
"trh",
"Gasp",
# "Pcp-1",
"Cpr35B",
"Cpr5C",
"Cpr11A",
"esg",
"Dl",
"bsh",
"eater",
"Hml"
)
```

# miniViolin

```{r miniViolin_set2}
for (gene in gene_list) {
  plot <- VlnPlot(EGFP, features = gene, pt.size = 0, combine = FALSE)
  p <- plot[[1]] +
    theme(legend.position = 'none') +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ylab(gene) +
    theme(plot.title = element_blank()) +
    theme(axis.text.y = element_text(size = 3)) +
    theme(text = element_text(size = 8))
  assign(gene, p)
}

# plot <- VlnPlot(EGFP, features = "Pcp-1", pt.size = 0, combine = FALSE)
# Pcp1 <- plot[[1]] +
#     theme(legend.position = 'none') +
#     theme(axis.title.x=element_blank(),
#           axis.text.x=element_blank(),
#           axis.ticks.x=element_blank()) +
#     ylab("Pcp-1") +
#     theme(plot.title = element_blank()) +
#     theme(axis.text.y = element_text(size = 3)) +
#     theme(text = element_text(size = 8))

x_label <- plot[[1]] +
  theme(legend.position = 'none') +
  ylab("") +
  theme(plot.title = element_blank()) +
  theme(axis.text.y = element_text(size = 3)) +
  theme(text = element_text(size = 8)) +
  theme(axis.text.x = element_text(size = 20))

plot_grid(
Mhc,
Mp20,
Act87E,
Act57B,
Mef2,
Cyp4g1,
Desat1,
CG18609,
CG17562,
btl,
trh,
Gasp,
# Pcp1,
Cpr35B,
Cpr5C,
Cpr11A,
esg,
Dl,
bsh,
eater,
Hml,
x_label, ncol = 1)
```

# Notes

2020-02-05:

  * miniViolin plots of known marker genes for all clusters.

Tue Dec 10, 2019:

  * Violin plot for EGFP and TSC separately for the last set of genes; Combined violin plot for the same; Combined dot plot for top 5 genes by fold change in all clusters (EGFP: Green and TSC: Red).

Wed Dec 5, 2019:

  * Removed three genes: Lsd-1, mdy, Fas1.

Wed Dec 4, 2019:

  * Use these selected genes for cluster 0, 1 and 2. Cluster 0: Pli, LpR2, path, apolpp, FASN1, Hnf4, Lsd-1, mdy; Cluster 1: sls, Mlc2, Mlp60A, Mhc, Mf, Mp20; Cluster 2: FASN3, FASN2, LpR1, salm, ImpL2, Fas1.

Sun Dec 1, 2019:

  * Dot plot and mini violin plots: 3 top expressed marker genes for dot plot; 2 top for mini-violin plot.

Tue Oct 29, 2019:

  * Use SoupX fixed 0.45 to remove ambient RNA.

Mon Oct 7, 2019:

  * Add more sequence depth.

Mon, Sep 30, 2019:

  * Remove genes: EGFP, Tsc1, gig. Then perform integrate analysis of EGFP, TSC1.

Fri, Sep 20, 2019:

  * First version for integrate analysis of EGFP, TSC1.

# Session Info

```{r sessioninfo, message=TRUE}
sessionInfo()
```

